---
title: "Accurate Inference of Genetic Ancestry from Cancer Sequencing"
author: Pascal Belleau, Astrid Deschênes and Alexander Krasnitz
output:
  BiocStyle::html_document:
    toc: true
bibliography: aicsBiblio.bibtex
vignette: >
  %\VignetteIndexEntry{Accurate Inference of Genetic Ancestry from Cancer Sequencing}
  %\VignettePackage{aicsPaper}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
  library(knitr)
  library(aicsPaper)
})

set.seed(121444)
```

<br />
**Package**: `r Rpackage("aicsPaper")`<br />
**Authors**: `r packageDescription("aicsPaper")[["Author"]]`<br />
**Version**: `r packageDescription("aicsPaper")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("aicsPaper")[["License"]]`<br />


# Licensing 

The `r Githubpkg("belleau/aicsPaper")` package and the underlying 
`r Githubpkg("belleau/aicsPaper")` code are distributed under  
the Artistic license 2.0. You are free to use and 
redistribute this software.  

<br>
<br>

# Citing

If you use this package for a publication, we would ask you to cite the 
following:

> Pascal Belleau, Astrid Deschênes, David A. Tuveson, Alexander Krasnitz. Accurate and robust inference of genetic ancestry from cancer-derived molecular data across genomic platforms. bioRxiv 2022.02.01.478737; doi: https://doi.org/10.1101/2022.02.01.478737 

<br>
<br>

# Introduction

Multiple methods have been implemented to infer ancestry from germline DNA 
sequence [@Price2006; @Pritchard2000; @Alexander2009]. However, genotyping of 
DNA from matched normal specimens is not part of standard clinical practice
and is not performed routinely outside academic clinical centers. 
In sum, matched germline DNA sequence is often missing for cancer-derived 
molecular data. In such cases, having the possibility to infer ancestry 
from tumor-derived data would be beneficial.

The **aicsPaper** package implements an inference procedure that has been
specifically developed to accurately infer genetic ancestry from 
cancer-derived sequencing. The covered cancer-derived sequencing are, more 
specifically, tumor exomes, targeted gene panels and RNA sequences.


<br>
<br>

# Installation

To install the latest version accessible on the 
[aicsPaper Github Website](https://github.com/belleau/aicsPaper "aicsPaper Github Site"), 
the `r CRANpkg("devtools")` package is required.

```{r installDemo01, eval=FALSE}
## Load required package
library(devtools)

## Install the latest version of aicsPaper
devtools::install_github('belleau/aicsPaper')
```

<br>
<br>



# Main Steps



<br>
<br>

## Formatting the information from 1000 Genomes (1KG)

### Create a predigree file in RDS format

First, the pedigree file with the description of the 1KG samples
needs to be downloaded from the 1KG ftp site:

> ftp://ftp.1000genomes.ebi.ac.uk/vol1/ftp/technical/working/20130606_sample_info/20130606_g1k.ped

Then, the function __prepPed1KG()__ is used to create the pedigree file 
in RDS format:

```{r prepPed1KG, eval=FALSE, echo=TRUE}
## Load required package
library(aicsPaper)

## The path to the pedigree file from 1KG
## In this example, the file is in the current directory
filePED1KGOri <- "20130606_g1k.ped"

## Extract needed information from the pedigree file from 1KG
ped <- prepPed1KG(filePED1KGOri)

## Save the pedigree information in a RDS file 
## In this example, the file is saved here ./data/metadata/ped1KG.rds
filePED1KG <- file.path("data", "metadata","ped1KG.rds")
saveRDS(ped,  filePED1KG)
    
```


<br>
<br>



# Session info

Here is the output of `sessionInfo()` on the system on which this document was 
compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>


# References

