---
title: "Population reference dataset GDS files (optional)"
author: Pascal Belleau, Astrid Deschênes and Alexander Krasnitz
output:
    BiocStyle::html_document:
        number_sections: yes
        toc: true
    pkgdown:
        number_sections: yes
        as_is: true
urlcolor: darkred
linkcolor: darkred
bibliography: aicsBiblio.bibtex
vignette: >
    %\VignetteIndexEntry{Population reference dataset GDS files (optional)}
    %\VignettePackage{RAIDS}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
    library(knitr)
    library(RAIDS)
})

set.seed(121444)
```

<br />
**Package**: `r Rpackage("RAIDS")`<br />
**Authors**: `r packageDescription("RAIDS")[["Author"]]`<br />
**Version**: `r packageDescription("RAIDS")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("RAIDS")[["License"]]`<br />


<br>
<br>




This section explains in further details the format of the population reference 
GDS files that are needed to run the ancestry inference tool. 

- Remove related samples


# Pre-processed files, from 1000 Genomes in hg38, are available

Pre-processed files used in the RAIDS associated publication, are 
available at this address:


[https://labshare.cshl.edu/shares/krasnitzlab/aicsPaper](https://labshare.cshl.edu/shares/krasnitzlab/aicsPaper)

Beware that some of those files are voluminous.

<br>
<br>

# Session info

Here is the output of `sessionInfo()` on the system on which this document was 
compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>

