---
title: "Population reference dataset GDS files"
author: Pascal Belleau, Astrid Deschênes and Alexander Krasnitz
output:
    BiocStyle::html_document:
        number_sections: yes
        toc: true
    pkgdown:
        number_sections: yes
        as_is: true
urlcolor: darkred
linkcolor: darkred
bibliography: aicsBiblio.bibtex
vignette: >
    %\VignetteIndexEntry{Population reference dataset GDS files}
    %\VignettePackage{RAIDS}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
BiocStyle::markdown()

suppressPackageStartupMessages({
    library(knitr)
    library(RAIDS)
    library(SNPRelate)
    library(gdsfmt)
})

set.seed(121444)
```

<br />
**Package**: `r Rpackage("RAIDS")`<br />
**Authors**: `r packageDescription("RAIDS")[["Author"]]`<br />
**Version**: `r packageDescription("RAIDS")$Version`<br />
**Compiled date**: `r Sys.Date()`<br />
**License**: `r packageDescription("RAIDS")[["License"]]`<br />


<br>
<br>




This section explains in further details the format of the population reference 
GDS files that are needed to run the ancestry inference tool. 

Three different files are generated from the reference dataset:

- The population reference GDS File
- The population reference SNV Annotation GDS file
- The population reference SNV Retained VCF file


# Population Reference GDS File


All related samples must be removed.

```{r runRefGDS, echo=TRUE, eval=TRUE, collapse=TRUE, warning=FALSE, message=FALSE}
#############################################################################
## Load required packages
#############################################################################
library(RAIDS)    
library(SNPRelate)

pathReference <- system.file("extdata/example/", package="RAIDS")

fileReferenceGDS <- file.path(pathReference, "gdsRef", "ex1kg.gds")

gdsRef <- snpgdsOpen(fileReferenceGDS)

## Show the file format
print(gdsRef)

closefn.gds(gdsRef)
```

# Population Reference Annotation GDS file


```{r runRefAnnotGDS, echo=TRUE, eval=TRUE, collapse=TRUE, warning=FALSE, message=FALSE}
#############################################################################
## Load required packages
#############################################################################
library(RAIDS)    
library(SNPRelate)

pathReference <- system.file("extdata/example/", package="RAIDS")

fileReferenceAnnotGDS <- file.path(pathReference, "gdsRef", "exAnnot1kg.gds")

gdsRefAnnot <- openfn.gds(fileReferenceAnnotGDS)

## Show the file format
print(gdsRefAnnot)

closefn.gds(gdsRefAnnot)
```


# Pre-processed files, from 1000 Genomes in hg38, are available

Pre-processed files used in the RAIDS associated publication, are 
available at this address:


[https://labshare.cshl.edu/shares/krasnitzlab/aicsPaper](https://labshare.cshl.edu/shares/krasnitzlab/aicsPaper)

Beware that some of those files are voluminous.

<br>
<br>

# Session info

Here is the output of `sessionInfo()` on the system on which this document was 
compiled:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

<br>
<br>

